\documentclass[letterpaper,10pt]{article}

% Dependencies
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{booktabs}

% Serif
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

%-----------------%
% Custom Commands %
%-----------------%

% Centered title along with subtitle between HR
% Usage: \documentTitle{Name}{Details}
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\scshape\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    %{\footnotesize\color{accentTitle} #2}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

% Create a footer with correct padding
% Usage: \documentFooter{\thepage of X}
\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

% Simple wrapper to set up page numbering
% Usage: \numberedPages
% WARNING: Must run pdflatex twice!
\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

% Section heading with horizontal rule
% Usage: \section{Title}
\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

% Section heading with separator and content on same line
% Usage: \tinysection{Title}
\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\scshape\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

% Indented line with arguments left/right aligned in document
% Usage: \heading{Left}{Right}
\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

% Adds \textbf to \heading
\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

% Adds \textit to \heading
\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

% Template for itemized lists
% Usage: \begin{resume_list} [items] \end{resume_list}
\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
  %\vspace{-2pt}
}

% Formats an item to use as an itemized title
% Usage: \itemTitle{Title}
\newcommand{\itemTitle}[1]{
  \item[] \underline{#1}\vspace{4pt}
}

% Bullets used in itemized lists
\renewcommand\labelitemi{--}

%% END_FILE: mteck.sty
%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

  %---------%
  % Heading %
  %---------%

  \documentTitle{Akanksha}{
    \href{https://www.linkedin.com/in/akanksha--thakur/}{\raisebox{-0.15\height} \faLinkedin\ linkedin.com/in/akanksha--thakur} ~
    \href{mailto:ak.t.kree@google.com}{\raisebox{-0.15\height} \faEnvelope\ ak.t.kree@google.com} ~
    \raisebox{-0.05\height} \faPhone\ 9779669457
  }
  

  %-----------%
  % Education %
  %-----------%

  \section{Education}

  \setlength{\tabcolsep}{15pt} % decrease the value if the content is overfitting
  \begin{tabular}{llll}
    \centering
    \toprule
    \textbf{Qualification}  & \textbf{Institute}    & \textbf{Year}     & \textbf{CGPA/\%} \\ 
    \toprule
    Aerospace Engineering & Punjab Engineering College  & 2021-2025   & 7.97\\ 
    Class XII (CBSE) & DR. Devi Chand D.A.V Public School  & 2021   & 95.6\%    \\ 
    Matriculation (CBSE) & DR. Devi Chand D.A.V Public School  & 2019   & 96.2\%   \\
    \bottomrule \\[-0.75cm]
  \end{tabular}
  \vspace{8pt}


  %--------%
  % Skills %
  %--------%

  \section{Technical Competencies}

  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=185pt]
    \item[\textbf{PROGRAMMING AND OTHER TOOLS}] Python, SQL, Tableau, PowerBI
    \item[\textbf{LIBRARIES AND FRAMEWORKS}] NumPy, Pandas, Scikit-Learn, MatPlotLib, BeautifulSoup, OpenCV, Tensorflow, Pytorch
    \item[\textbf{AREAS OF INTEREST}] Natural Language Processing (NLP),
    Machine Learning, Deep Learning, Data Analysis, Statistics
  \end{itemize}


  %------------%
  % Experience %
  %------------%

  \section{Experience}

  \headingBf{POSE ESTIMATION OF NON-COOPERATIVE SPACECRAFTS | CSIR-CSIO}{Research Internship}
  \textit{Computer Vision • Deep Learning • Deep Neural Networks • Image Processing • CNN • RNN • Transformers}
  \headingIt{Jan 2024 - Present}{}
  \begin{resume_list}
    \item Studied various architectures (both CNN and transformer-based) for Vision tasks. In-depth discussions with my mentor and the principal scientist. Hands-on experience with coding and implementation.
  \end{resume_list}

  \vspace{1em}


   %------------%
  % PROJECTS %
  %------------%
  \section{Academic Projects}
  \headingBf{INCORPORATION OF COMPUTER VISION IN SURVEILLANCE UAV FUNCTIONING}{Minor Project}
  \textit{Computer Vision • Deep Learning • Machine Learning • Image Processing}
  \headingIt{Sept 2023 - Nov 2023}{}
  \begin{resume_list}
    \item This particular project is designed with the explicit objective of addressing real-world challenges, with its practical application centered around the simulation of a Vision-Based Surveillance Unmanned Aerial Vehicle (UAV).
  \end{resume_list}

  \vspace{1em}

  \headingBf{NLP AND DATA ANALYSIS}{}
  \textit{NLP • Data Visualization}
  \headingIt{Oct 2023 – Oct 2023}{}
  \begin{resume_list}
    \item Utilized cosine distance to compute vector similarity, subsequently categorizing inferences into distinct categories: High (H), Intermediate-High (H/I), Intermediate (I), and Low (L). Devised a set of targeted questions prioritizing both relevance and clarity for enhanced project understanding and communication.
  \end{resume_list}
  

  %----------------------------%
  % Extracurricular Activities %
  %----------------------------%

  \section{Positions Of Responsibility and Extracurricular Interests}

  \begin{resume_list}
    \item \textbf{Marketing intern - VONG (Voice of New Generation) NGO:} Interacting with school kids for awareness regarding sustainability. Formulating and implementing marketing strategies.
    \item \textbf{Sub Head - Battle of Bands, PECFEST:} Organizing and Managing the event.
    \item \textbf{PEC Music Club:} Organized and managed \textbf{more than 30} events, and awarded \textbf{Certificate of Appreciation} by the college.

  \end{resume_list}
\end{document}
